```{r echo=FALSE, warning=FALSE, message=FALSE}
# Library
library(ggplot2)
library(tidyverse)
library(janitor)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
datasepa_data <- read_csv('data_preparation/sepdata_arrivel.csv')
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
cycle <- read_csv("data_preparation/stations.csv")
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
cluster1 <- read_csv("table/nonscaled/cluster1.csv") %>% 
  select(., c(1, 2))
cluster2 <- read_csv("table/nonscaled/cluster2.csv") %>% 
  select(., c(1, 2))
cluster3 <- read_csv("table/nonscaled/cluster3.csv") %>% 
  select(., c(1, 2))
cluster4 <- read_csv("table/nonscaled/cluster4.csv") %>% 
  select(., c(1, 2))
cluster5 <- read_csv("table/nonscaled/cluster5.csv") %>% 
  select(., c(1, 2))
cluster6 <- read_csv("table/nonscaled/cluster6.csv") %>% 
  select(., c(1, 2))
```


```{r}
n <- nrow(cluster1) +nrow(cluster2)+nrow(cluster3)+nrow(cluster4)+nrow(cluster5)+nrow(cluster6)
n
```

### Function for extracting data for month 1

```{r}
countdata1fun <- function(data, m, y, n1, n2){
  alldatamonth <- data %>%
    filter(month == m) #'03'
  
  alldatamonth$day <- as.numeric(alldatamonth$day)
  monthlast <- alldatamonth %>% 
    filter(day >= n1) %>% 
    filter(day <= n2)
  

  monthlastyear <- monthlast %>%
    filter(year == y)
  
  return(monthlastyear)
 
}
```

### Function for extracting data for month 2

```{r}
countdatafun <- function(cluster, m, y, n1, n2){
  clusterdf <- cluster %>% 
  left_join(., datasepa_data,
            by = c("id" = "end_station_id")) %>% 
  select(., c(3:9, 1, 2, 11))
  alldatamonth <- clusterdf %>%
    filter(month == m) #'03'
  
  alldatamonth$day <- as.numeric(alldatamonth$day)
  monthlast <- alldatamonth %>% 
    filter(day >= n1) %>% 
    filter(day <= n2)
  

  monthlastyear <- monthlast %>%
    filter(year == y)
  
  return(monthlastyear)
 
}
```


### Function for plot weekly chart 1

```{r}
chart1fun <- function(data, m, y, n1, n2,
                     a, b, c, d, e, f, g, filename){
  monthlastyear <- countdata1fun(data, m, y, n1, n2)
  # chart weekly data
  monthlastyear <- monthlastyear %>%
    group_by(day, hour) %>%
    summarise(daily_trip=sum(count))
  
  monthlastyear$day <- str_replace_all(monthlastyear$day, a, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, b, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, c, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, d, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, e, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, f, "2") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, g, "2") 
  
  monthlastyear <- monthlastyear %>%
    group_by(day, hour) %>%
    summarise(daily_trip= mean(daily_trip))
  
  monthlastyear$day <- as.character(monthlastyear$day)
  
  cbPalette <- c("#0432FF", "#FF0000")
  monthlastyear$hour <- as.numeric(monthlastyear$hour)
  monthlastyear %>%
    ggplot( aes(x=hour, y=daily_trip, group = day, 
                color = day,shape = day)) +
    geom_point(size = 2.2) + 
    geom_line(size = 1.8) +
    theme_linedraw() + 
    scale_color_manual(values=cbPalette)+
    scale_x_continuous (breaks = c(4, 8, 12, 16, 20))+
    ylim(0, 6000)
  
    ggsave(filename, width = 8, height = 6) 
}
```

### Function for plot weekly chart 2

```{r}
chartfun <- function(cluster, m, y, n1, n2,
                     a, b, c, d, e, f, g, filename){
  countmonth <- countdatafun(cluster, m, y, n1, n2)
  # chart weekly data
  monthlastyear <- countmonth %>%
    group_by(day, hour) %>%
    summarise(daily_trip=sum(count))
  
  monthlastyear$day <- str_replace_all(monthlastyear$day, a, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, b, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, c, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, d, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, e, "1") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, f, "2") 
  monthlastyear$day <- str_replace_all(monthlastyear$day, g, "2") 
  
  monthlastyear <- monthlastyear %>%
    group_by(day, hour) %>%
    summarise(daily_trip= mean(daily_trip))
  
  monthlastyear$day <- as.character(monthlastyear$day)
  
  cbPalette <- c("#0432FF", "#FF0000")
  monthlastyear$hour <- as.numeric(monthlastyear$hour)
  monthlastyear %>%
    ggplot( aes(x=hour, y=daily_trip, group = day, 
                color = day,shape = day)) +
    geom_point(size = 2.2) + 
    geom_line(size = 1.8) +
    theme_linedraw() + 
    scale_color_manual(values=cbPalette)+
    scale_x_continuous (breaks = c(4, 8, 12, 16, 20))+
    ylim(0, 2200)
  
    ggsave(filename, width = 8, height = 6) 
    
    return(countmonth)
}
```

### overall pattern
#### run 2019 data for all data

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chart1fun(datasepa_data, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019mar.jpg")
chartmay <- chart1fun(datasepa_data, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019may.jpg")
chartaug <- chart1fun(datasepa_data, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019aug.jpg")
```

#### run 2020 data for all data

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chart1fun(datasepa_data, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020mar.jpg")
chartmay <- chart1fun(datasepa_data, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020may.jpg")
chartaug <- chart1fun(datasepa_data, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020aug.jpg")
```

#### run 2021 data for all data

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chart1fun(datasepa_data, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021mar.jpg")
```


### cluster 1
#### run 2019 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster1, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster1.jpg")
chartmay <- chartfun(cluster1, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster1.jpg")
chartaug <- chartfun(cluster1, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster1.jpg")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/1/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/1/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/1/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster1, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster1.jpg")
chartmay <- chartfun(cluster1, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster1.jpg")
chartaug <- chartfun(cluster1, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster1.jpg")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/1/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/1/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/1/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster1, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster1.jpg")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/1/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 2

#### run 2019 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster2, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster2.jpg")
chartmay <- chartfun(cluster2, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster2.jpg")
chartaug <- chartfun(cluster2, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster2.jpg")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/2/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/2/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/2/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster2, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster2.jpg")
chartmay <- chartfun(cluster2, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster2.jpg")
chartaug <- chartfun(cluster2, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster2.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/2/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/2/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/2/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster2, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster2.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/2/mar2021_2.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 3
#### run 2019 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster3, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster3.jpg")
chartmay <- chartfun(cluster3, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster3.jpg")
chartaug <- chartfun(cluster3, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster3.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/3/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/3/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/3/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster3, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster3.jpg")
chartmay <- chartfun(cluster3, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster3.jpg")
chartaug <- chartfun(cluster3, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster3.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/3/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/3/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/3/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster3, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster3.jpg")
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/3/mar2021_3.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 4
#### run 2019 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster4, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster4.jpg")
chartmay <- chartfun(cluster4, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster4.jpg")
chartaug <- chartfun(cluster4, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster4.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/4/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/4/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/4/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster4, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster4.jpg")
chartmay <- chartfun(cluster4, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster4.jpg")
chartaug <- chartfun(cluster4, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster4.jpg")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/4/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/4/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/4/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster4, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster4.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/4/mar2021_4.csv",row.names=FALSE,col.names=TRUE,sep=",")

```




### cluster 5
#### run 2019 data for cluster 5

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster5, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster5.jpg")
chartmay <- chartfun(cluster5, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster5.jpg")
chartaug <- chartfun(cluster5, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster5.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/5/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/5/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/5/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 5

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster5, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster5.jpg")
chartmay <- chartfun(cluster5, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster5.jpg")
chartaug <- chartfun(cluster5, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster5.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/5/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/5/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/5/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 5

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster5, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster5.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/5/mar2021_5.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


### cluster 6
#### run 2019 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}
# cluster, m, y, n1, n2,a, b, c, d, e, f, g, filename

chartmar <- chartfun(cluster6, "03", "2019", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31",
                     "pic/temporal_chart/dailytrip2019marcluster6.jpg")
chartmay <- chartfun(cluster6, "05", "2019", 20, 26,
                     "20", "21", "22", "23", "24", "25", "26",
                     "pic/temporal_chart/dailytrip2019maycluster6.jpg")
chartaug <- chartfun(cluster6, "08", "2019", 19, 25,
                     "19", "20", "21", "22", "23", "24", "25",
                     "pic/temporal_chart/dailytrip2019augcluster6.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/6/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/6/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/6/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}
chartmar <- chartfun(cluster6, "03", "2020", 23, 29,
                     "23", "24", "25", "26", "27", "28", "29",
                     "pic/temporal_chart/dailytrip2020marcluster6.jpg")
chartmay <- chartfun(cluster6, "05", "2020", 25, 31,
                     "25", "26", "27", "28", "29", "30", "31", 
                     "pic/temporal_chart/dailytrip2020maycluster6.jpg")
chartaug <- chartfun(cluster6, "08", "2020", 24, 30, 
                     "24", "25", "26", "27", "28", "29", "30", 
                     "pic/temporal_chart/dailytrip2020augcluster6.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/6/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- chartmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/6/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- chartaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/6/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2021 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}

chartmar <- chartfun(cluster6, "03", "2021", 22, 28,
                     "22", "23", "24", "25", "26", "27", "28",
                     "pic/temporal_chart/dailytrip2021marcluster6.jpg")
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- chartmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/6/mar2021_6.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

