```{r echo=FALSE, warning=FALSE, message=FALSE}
# Library
library(ggplot2)
library(tidyverse)
library(janitor)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
datasepa_data <- read_csv('data_preparation/sepdata_arrivel.csv')
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
cycle <- read_csv("data_preparation/stations.csv")
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
cluster1 <- read_csv("table/nonscaled/cluster1.csv") %>% 
  select(., c(1, 2))
cluster2 <- read_csv("table/nonscaled/cluster2.csv") %>% 
  select(., c(1, 2))
cluster3 <- read_csv("table/nonscaled/cluster3.csv") %>% 
  select(., c(1, 2))
cluster4 <- read_csv("table/nonscaled/cluster4.csv") %>% 
  select(., c(1, 2))
cluster5 <- read_csv("table/nonscaled/cluster5.csv") %>% 
  select(., c(1, 2))
cluster6 <- read_csv("table/nonscaled/cluster6.csv") %>% 
  select(., c(1, 2))
```

### Function for extracting data for month

```{r}
countdatafun <- function(cluster, m, y, n1, n2){
  clusterdf <- cluster %>% 
    left_join(., datasepa_data,
              by = c("id" = "end_station_id")) %>% 
    select(., c(3:9, 1, 2, 11))
  alldatamonth <- clusterdf %>%
    filter(month == m) #'03'
  
  alldatamonth$day <- as.numeric(alldatamonth$day)
  monthlast <- alldatamonth %>% 
    filter(day >= n1) %>% 
    filter(day <= n2)
  

  monthlastyear <- monthlast %>%
    filter(year == y)
  
  return(monthlastyear)
 
}
```


### cluster 1
#### run 2019 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster1, "03", "2019", 25, 29)
countmay <- countdatafun(cluster1, "05", "2019", 20, 24)
countaug <- countdatafun(cluster1, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/1/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/1/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/1/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster1, "03", "2019", 30, 31)
countmay <- countdatafun(cluster1, "05", "2019", 25, 26)
countaug <- countdatafun(cluster1, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/1/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/1/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/1/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster1, "03", "2020", 23, 27)
countmay <- countdatafun(cluster1, "05", "2020", 25, 29)
countaug <- countdatafun(cluster1, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/1/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/1/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/1/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster1, "03", "2020", 28, 29)
countmay <- countdatafun(cluster1, "05", "2020", 30, 31)
countaug <- countdatafun(cluster1, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/1/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/1/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/1/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster1, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/1/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster1, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/1/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


### cluster 2

#### run 2019 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster2, "03", "2019", 25, 29)
countmay <- countdatafun(cluster2, "05", "2019", 20, 24)
countaug <- countdatafun(cluster2, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/2/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/2/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/2/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster2, "03", "2019", 30, 31)
countmay <- countdatafun(cluster2, "05", "2019", 25, 26)
countaug <- countdatafun(cluster2, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/2/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/2/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/2/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster2, "03", "2020", 23, 27)
countmay <- countdatafun(cluster2, "05", "2020", 25, 29)
countaug <- countdatafun(cluster2, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/2/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/2/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/2/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster2, "03", "2020", 28, 29)
countmay <- countdatafun(cluster2, "05", "2020", 30, 31)
countaug <- countdatafun(cluster2, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/2/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/2/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/2/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 2

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster2, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/2/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster2, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/2/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 3
#### run 2019 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster3, "03", "2019", 25, 29)
countmay <- countdatafun(cluster3, "05", "2019", 20, 24)
countaug <- countdatafun(cluster3, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/3/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/3/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/3/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster3, "03", "2019", 30, 31)
countmay <- countdatafun(cluster3, "05", "2019", 25, 26)
countaug <- countdatafun(cluster3, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/3/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/3/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/3/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster3, "03", "2020", 23, 27)
countmay <- countdatafun(cluster3, "05", "2020", 25, 29)
countaug <- countdatafun(cluster3, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/3/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/3/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/3/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster3, "03", "2020", 28, 29)
countmay <- countdatafun(cluster3, "05", "2020", 30, 31)
countaug <- countdatafun(cluster3, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/3/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/3/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/3/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 3

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster3, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/3/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster3, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/3/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 4
#### run 2019 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster4, "03", "2019", 25, 29)
countmay <- countdatafun(cluster4, "05", "2019", 20, 24)
countaug <- countdatafun(cluster4, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/4/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/4/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/4/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster4, "03", "2019", 30, 31)
countmay <- countdatafun(cluster4, "05", "2019", 25, 26)
countaug <- countdatafun(cluster4, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/4/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/4/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/4/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster4, "03", "2020", 23, 27)
countmay <- countdatafun(cluster4, "05", "2020", 25, 29)
countaug <- countdatafun(cluster4, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/4/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/4/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/4/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster4, "03", "2020", 28, 29)
countmay <- countdatafun(cluster4, "05", "2020", 30, 31)
countaug <- countdatafun(cluster4, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/4/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/4/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/4/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 4

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster4, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/4/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster4, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/4/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 5
#### run 2019 data for cluster 1

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster5, "03", "2019", 25, 29)
countmay <- countdatafun(cluster5, "05", "2019", 20, 24)
countaug <- countdatafun(cluster5, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/5/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/5/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/5/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster5, "03", "2019", 30, 31)
countmay <- countdatafun(cluster5, "05", "2019", 25, 26)
countaug <- countdatafun(cluster5, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/5/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/5/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/5/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 5

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster5, "03", "2020", 23, 27)
countmay <- countdatafun(cluster5, "05", "2020", 25, 29)
countaug <- countdatafun(cluster5, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/5/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/5/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/5/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster5, "03", "2020", 28, 29)
countmay <- countdatafun(cluster5, "05", "2020", 30, 31)
countaug <- countdatafun(cluster5, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/5/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/5/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/5/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 5

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster5, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/5/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster5, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/5/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

### cluster 6
#### run 2019 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster6, "03", "2019", 25, 29)
countmay <- countdatafun(cluster6, "05", "2019", 20, 24)
countaug <- countdatafun(cluster6, "08", "2019", 19, 23)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekdays/6/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekdays/6/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekdays/6/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster6, "03", "2019", 30, 31)
countmay <- countdatafun(cluster6, "05", "2019", 25, 26)
countaug <- countdatafun(cluster6, "08", "2019", 24, 25)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2019 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2019,"table/qgis_visualization_csv_files/weekends/6/mar2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2019 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2019,"table/qgis_visualization_csv_files/weekends/6/may2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2019 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2019,"table/qgis_visualization_csv_files/weekends/6/aug2019.csv",row.names=FALSE,col.names=TRUE,sep=",")

```

#### run 2020 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster6, "03", "2020", 23, 27)
countmay <- countdatafun(cluster6, "05", "2020", 25, 29)
countaug <- countdatafun(cluster6, "08", "2020", 24, 28)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekdays/6/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekdays/6/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekdays/6/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar <- countdatafun(cluster6, "03", "2020", 28, 29)
countmay <- countdatafun(cluster6, "05", "2020", 30, 31)
countaug <- countdatafun(cluster6, "08", "2020", 29, 30)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2020 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2020,"table/qgis_visualization_csv_files/weekends/6/mar2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

may2020 <- countmay %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(may2020,"table/qgis_visualization_csv_files/weekends/6/may2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

aug2020 <- countaug %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(aug2020,"table/qgis_visualization_csv_files/weekends/6/aug2020.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


#### run 2021 data for cluster 6

```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster6, "03", "2021", 22, 26)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekdays/6/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```
```{r echo=FALSE, warning=FALSE, message=FALSE}
countmar <- countdatafun(cluster6, "03", "2021", 27, 28)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
mar2021 <- countmar %>% 
  group_by(id) %>% 
  summarise(trip=sum(count),
            duration=mean(duration)) %>% 
  left_join(., cycle, by = c("id" = "id"))
write.table(mar2021,"table/qgis_visualization_csv_files/weekends/6/mar2021_1.csv",row.names=FALSE,col.names=TRUE,sep=",")

```


