
## Statistical properties of bicycle shaeing mobility network

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Library
library(tidyverse)
library(janitor)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
datasepa_data <- read_csv('data_preparation/sepdata_departure.csv')
```

## Function for extracting and calculating data for month 

```{r}
countdatafun <- function(data, m, y, n1, n2){
  alldatamonth <- data %>%
    filter(month == m) #'03'
  
  alldatamonth$day <- as.numeric(alldatamonth$day)
  monthlast <- alldatamonth %>% 
    filter(day >= n1) %>% 
    filter(day <= n2)
  

  monthlastyear <- monthlast %>%
    filter(year == y)
  
  countmonyear <- monthlastyear %>%
    group_by(end_station_id, start_station_id,end_station_name, start_station_name) %>%
    summarise(route=sum(count))
  
  return(countmonyear)
 
}
```

## calculation for weekdays

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar2019 <- countdatafun(datasepa_data, "03", "2019", 25, 29)
countmay2019 <- countdatafun(datasepa_data, "05", "2019", 20, 24)
countaug2019 <- countdatafun(datasepa_data, "08", "2019", 19, 23)
countmar2020 <- countdatafun(datasepa_data, "03", "2020", 23, 27)
countmay2020 <- countdatafun(datasepa_data, "05", "2020", 25, 29)
countaug2020 <- countdatafun(datasepa_data, "08", "2020", 24, 28)
countmar2021 <- countdatafun(datasepa_data, "03", "2021", 22, 26)
```

### N total number of nodes

```{r}
nodefun <- function(countmonth){
  ndf1 <- countmonth %>%
    dplyr::select(., c(1, 3, 5)) %>% 
    rename("station_id"="end_station_id", 
           "station_name"="end_station_name")
  ndf2 <- countmonth %>%
    dplyr::select(., c(2, 4, 5))%>% 
    rename("station_id"="start_station_id", 
           "station_name"="start_station_name")
  ndf <- rbind(ndf1, ndf2) %>% 
    group_by(station_name, station_id) %>%
    summarise(f=sum(route)/5)
  return(ndf)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
nodemay2019 <- nodefun(countmay2019) #790
nodemay2020 <- nodefun(countmay2020) #781
nodeaug2019 <- nodefun(countaug2019) #780
nodeaug2020 <- nodefun(countaug2020) #783
nodemar2019 <- nodefun(countmar2019) #785
nodemar2020 <- nodefun(countmar2020) #783
nodemar2021 <- nodefun(countmar2021) #790
```

### L total number of links

```{r}
L/5/2
# countmay2019 : 87025
# countmay2020 : 86457
# countaug2019 : 79206
# countaug2020 : 71657
# countmar2019 : 73606
# countmar2020 : 28976
# countmar2021 : 55059

# 8702.5, 8645.7, 7920.6, 7165.7, 7360.6, 2897.6, 5505.9
```

### T total number of trips

```{r}
totalfun <- function(countmonth){
  
  totaltrip <- countmonth %>% 
    cbind(., 1) 
  
  totaltrip <- totaltrip %>% 
    rename("base" = "...6") %>% 
    group_by (base) %>% 
    summarise(count=sum(route)/5)
  return(totaltrip)
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
tmay2019 <- totalfun(countmay2019) # 36955
tmay2020 <- totalfun(countmay2020) # 40458
taug2019 <- totalfun(countaug2019) # 34163
taug2020 <- totalfun(countaug2020) # 27650
tmar2019 <- totalfun(countmar2019) # 30527
tmar2020 <- totalfun(countmar2020) # 10015
tmar2021 <- totalfun(countmar2021) # 20365
```


### mean at node
    
    <F> mean node flux (trips T/N) 
    <k> mean **node degree** (links L/N)
    <w> mean edge weight (trips on link F/k)


### coefficient of variation (CV)


    CV(F) = sd(F)/mean(F)

    CV(k) = sd(k)/mean(k)

    CV(w) = sd(w)/mean(w)

```{r}
calfun <- function(year, t, l, n){
  year = year
  t = t
  l = l
  n = n
  df = data.frame(year, t, l, n)
  df$t <- as.numeric(df$t)
  df$l <- as.numeric(df$l)
  df$n <- as.numeric(df$n)
  
  df <- df %>% 
    mutate(f = t/n) %>% 
    mutate(k = l/n) %>% 
    mutate(w = f/k) %>% 
     
    mutate(across(is.numeric, round, 2))
  return(df)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df <- calfun(c("2019-05","2020-05","2019-08","2020-08",
               "2019-03","2020-03","2021-03"),
             c("36955","40458","34163","27650",
               "30527","10015","20365"),
             c("8702.5", "8645.7", "7920.6", "7165.7", "7360.6", "2897.6", "5505.9"),
             c("790","781","780","783","785","783","790"))
```
```{r}
dfyear <- t(data.frame(df, row.names=1))
```

The node flux F: the total number of trips that either start from or end at the node.

```{r}
f_fun <- function(nodefun){
  
  f <- nodefun %>% 
    cbind(., 1) %>% 
    rename("base" = "...4") %>% #check the column name
    group_by (base) %>% 
    summarise(cvf = sd(f)/mean(f))%>%
    mutate(across(is.numeric, round, 2))
  return(f)
}
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
fmay2019 <- f_fun(nodemay2019) #0.74
fmay2020 <- f_fun(nodemay2020) #0.83
faug2019 <- f_fun(nodeaug2019) #0.78
faug2020 <- f_fun(nodeaug2020) #0.64
fmar2019 <- f_fun(nodemar2019) #0.80
fmar2020 <- f_fun(nodemar2020) #0.63
fmar2021 <- f_fun(nodemar2021) #0.64
```

```{r}
nodedegreefun <- function(countmonth){
  
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  nodedegree <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/10)%>% 
    mutate(across(is.numeric, round, 2))
  return(nodedegree)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
cycle <- read_csv("data_preparation/stations.csv") %>% 
  select(., c(2, 3, 4))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
kmay2019n <- nodedegreefun(countmay2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))

kmay2020n <- nodedegreefun(countmay2020) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kaug2019n <- nodedegreefun(countaug2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kaug2020n <- nodedegreefun(countaug2020) %>%
  left_join(cycle, ., by = c("name" = "station_name"))

kmar2019n <- nodedegreefun(countmar2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kmar2020n <- nodedegreefun(countmar2020) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kmar2021n <- nodedegreefun(countmar2021) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
```

```{r}
write.table(kmay2019n,"table/qgis_nodedegree/weekdays/nodedegree201905.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmay2020n,"table/qgis_nodedegree/weekdays/nodedegree202005.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kaug2019n,"table/qgis_nodedegree/weekdays/nodedegree201908.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kaug2020n,"table/qgis_nodedegree/weekdays/nodedegree202008.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2019n,"table/qgis_nodedegree/weekdays/nodedegree201903.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2020n,"table/qgis_nodedegree/weekdays/nodedegree202003.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2021n,"table/qgis_nodedegree/weekdays/nodedegree202103.csv",row.names=FALSE,col.names=TRUE,sep=",")
```

```{r}
k_fun <- function(countmonth){
  
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  kdf <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/10)%>% 
    cbind(., 1) %>% 
    rename("base" = "1") %>% #check the column name
    group_by (base) %>% 
    summarise(cvk = sd(k)/mean(k))%>%
    mutate(across(is.numeric, round, 2))
  return(kdf)
}
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
kmay2019 <- k_fun(countmay2019) #0.52
kmay2020 <- k_fun(countmay2020) #0.60
kaug2019 <- k_fun(countaug2019) #0.53
kaug2020 <- k_fun(countaug2020) #0.54
kmar2019 <- k_fun(countmar2019) #0.54
kmar2020 <- k_fun(countmar2020) #0.62
kmar2021 <- k_fun(countmar2021) #0.55
```

```{r}
w_fun <- function(nodefun, countmonth){
  f <- nodefun 
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  wdf <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/10)%>% 
    left_join(., f, by = c("station_name" = "station_name")) %>% 
    mutate(w = f/k) %>% 
    cbind(., 1) %>% 
    rename("base" = "1") %>% #check the column name
    group_by (base) %>% 
    summarise(cvw = sd(w)/mean(w))%>%
    mutate(across(is.numeric, round, 2))
  return(wdf)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
wmay2019 <- w_fun(nodemay2019,countmay2019) #0.52
wmay2020 <- w_fun(nodemay2020,countmay2020) #0.43
waug2019 <- w_fun(nodeaug2019,countaug2019) #0.53
waug2020 <- w_fun(nodeaug2020,countaug2020) #0.45
wmar2019 <- w_fun(nodemar2019,countmar2019) #0.54
wmar2020 <- w_fun(nodemar2020,countmar2020) #0.42
wmar2021 <- w_fun(nodemar2021,countmar2021) #0.43
```
   


## calculation for weekends

```{r echo=FALSE, warning=FALSE, message=FALSE}

countmar2019 <- countdatafun(datasepa_data, "03", "2019", 30, 31)
countmay2019 <- countdatafun(datasepa_data, "05", "2019", 25, 26)
countaug2019 <- countdatafun(datasepa_data, "08", "2019", 24, 25)
countmar2020 <- countdatafun(datasepa_data, "03", "2020", 28, 29)
countmay2020 <- countdatafun(datasepa_data, "05", "2020", 30, 31)
countaug2020 <- countdatafun(datasepa_data, "08", "2020", 29, 30)
countmar2021 <- countdatafun(datasepa_data, "03", "2021", 27, 28)
```

### N total number of nodes

```{r}
nodefun <- function(countmonth){
  ndf1 <- countmonth %>%
    dplyr::select(., c(1, 3, 5)) %>% 
    rename("station_id"="end_station_id", 
           "station_name"="end_station_name")
  ndf2 <- countmonth %>%
    dplyr::select(., c(2, 4, 5))%>% 
    rename("station_id"="start_station_id", 
           "station_name"="start_station_name")
  ndf <- rbind(ndf1, ndf2) %>% 
    group_by(station_name, station_id) %>%
    summarise(f=sum(route)/2)
  return(ndf)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
nodemay2019 <- nodefun(countmay2019) #788
nodemay2020 <- nodefun(countmay2020) #781
nodeaug2019 <- nodefun(countaug2019) #778
nodeaug2020 <- nodefun(countaug2020) #778
nodemar2019 <- nodefun(countmar2019) #785
nodemar2020 <- nodefun(countmar2020) #781
nodemar2021 <- nodefun(countmar2021) #789
```

### L total number of links

```{r}
L/2/2
# countmay2019 : 30825
# countmay2020 : 59857
# countaug2019 : 30357
# countaug2020 : 35029
# countmar2019 : 28635
# countmar2020 : 12278
# countmar2021 : 34087

# 7706.25, 14964.25, 7589.25, 8757.25, 7158.75, 3069.5, 8521.75
```

### T total number of trips

```{r}
totalfun <- function(countmonth){
  
  totaltrip <- countmonth %>% 
    cbind(., 1) 
  
  totaltrip <- totaltrip %>% 
    rename("base" = "...6") %>% 
    group_by (base) %>% 
    summarise(count=sum(route)/2)
  return(totaltrip)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
tmay2019 <- totalfun(countmay2019) #25112
tmay2020 <- totalfun(countmay2020) #57422
taug2019 <- totalfun(countaug2019) #15970
taug2020 <- totalfun(countaug2020) #27672
tmar2019 <- totalfun(countmar2019) #22396
tmar2020 <- totalfun(countmar2020) #8924
tmar2021 <- totalfun(countmar2021) #27522
```


### mean at node
    
    <F> mean node flux (trips T/N) 
    <k> mean **node degree** (links L/N)
    <w> mean edge weight (trips on link F/k)


### coefficient of variation (CV)


    CV(F) = sd(F)/mean(F)

    CV(k) = sd(k)/mean(k)

    CV(w) = sd(w)/mean(w)

```{r}
calfun <- function(year, t, l, n){
  year = year
  t = t
  l = l
  n = n
  df = data.frame(year, t, l, n)
  df$t <- as.numeric(df$t)
  df$l <- as.numeric(df$l)
  df$n <- as.numeric(df$n)
  
  df <- df %>% 
    mutate(f = t/n) %>% 
    mutate(k = l/n) %>% 
    mutate(w = f/k) %>% 
     
    mutate(across(is.numeric, round, 2))
  return(df)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df2 <- calfun(c("2019-05","2020-05","2019-08","2020-08",
               "2019-03","2020-03","2021-03"),
             c("25112","57422","15970","27672",
               "22396","8924","27522"),
             c("7706.25", "14964.25", "7589.25", "8757.25", "7158.75", "3069.5", "8521.75"),
             c("788","781","778","778","785","781","789"))
```
```{r}
dfyear2 <- t(data.frame(df2, row.names=1))
```

The node flux F: the total number of trips that either start from or end at the node.

```{r}
f_fun <- function(nodefun){
  
  f <- nodefun %>% 
    cbind(., 1) %>% 
    rename("base" = "...4") %>% #check the column name
    group_by (base) %>% 
    summarise(cvf = sd(f)/mean(f))%>%
    mutate(across(is.numeric, round, 2))
  return(f)
}
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
fmay2019 <- f_fun(nodemay2019) #0.90
fmay2020 <- f_fun(nodemay2020) #0.90
faug2019 <- f_fun(nodeaug2019) #1.06
faug2020 <- f_fun(nodeaug2020) #0.81
fmar2019 <- f_fun(nodemar2019) #0.86
fmar2020 <- f_fun(nodemar2020) #0.73
fmar2021 <- f_fun(nodemar2021) #0.89
```

```{r}
nodedegreefun <- function(countmonth){
  
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  nodedegree <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/4)%>% 
    mutate(across(is.numeric, round, 2))
  return(nodedegree)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
cycle <- read_csv("data_preparation/stations.csv") %>% 
  select(., c(2, 3, 4))
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
kmay2019n <- nodedegreefun(countmay2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))

kmay2020n <- nodedegreefun(countmay2020) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kaug2019n <- nodedegreefun(countaug2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kaug2020n <- nodedegreefun(countaug2020) %>%
  left_join(cycle, ., by = c("name" = "station_name"))

kmar2019n <- nodedegreefun(countmar2019) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kmar2020n <- nodedegreefun(countmar2020) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
kmar2021n <- nodedegreefun(countmar2021) %>% 
  left_join(cycle, ., by = c("name" = "station_name"))
```

```{r}
write.table(kmay2019n,"table/qgis_nodedegree/weekends/nodedegree201905.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmay2020n,"table/qgis_nodedegree/weekends/nodedegree202005.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kaug2019n,"table/qgis_nodedegree/weekends/nodedegree201908.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kaug2020n,"table/qgis_nodedegree/weekends/nodedegree202008.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2019n,"table/qgis_nodedegree/weekends/nodedegree201903.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2020n,"table/qgis_nodedegree/weekends/nodedegree202003.csv",row.names=FALSE,col.names=TRUE,sep=",")
write.table(kmar2021n,"table/qgis_nodedegree/weekends/nodedegree202103.csv",row.names=FALSE,col.names=TRUE,sep=",")
```

```{r}
k_fun <- function(countmonth){
  
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  kdf <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/4)%>% 
    cbind(., 1) %>% 
    rename("base" = "1") %>% #check the column name
    group_by (base) %>% 
    summarise(cvk = sd(k)/mean(k))%>%
    mutate(across(is.numeric, round, 2))
  return(kdf)
}
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
kmay2019 <- k_fun(countmay2019) #0.63
kmay2020 <- k_fun(countmay2020) #0.69
kaug2019 <- k_fun(countaug2019) #0.66
kaug2020 <- k_fun(countaug2020) #0.64
kmar2019 <- k_fun(countmar2019) #0.64
kmar2020 <- k_fun(countmar2020) #0.74
kmar2021 <- k_fun(countmar2021) #0.67
```

```{r}
w_fun <- function(nodefun, countmonth){
  f <- nodefun 
  k <- countmonth %>% 
    cbind(., 1) %>% 
    rename("base" = 1) 
    
  kdf1 <- k %>%
    dplyr::select(., c(3, 6)) %>% 
    rename( "station_name"="end_station_name")
  kdf2 <- k %>%
    dplyr::select(., c(4, 6))%>% 
    rename("station_name"="start_station_name")
  wdf <- rbind(kdf1, kdf2) %>% 
    group_by(station_name) %>%
    summarise(k=sum(base)/4)%>% 
    left_join(., f, by = c("station_name" = "station_name")) %>% 
    mutate(w = f/k) %>% 
    cbind(., 1) %>% 
    rename("base" = "1") %>% #check the column name
    group_by (base) %>% 
    summarise(cvw = sd(w)/mean(w))%>%
    mutate(across(is.numeric, round, 2))
  return(wdf)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
wmay2019 <- w_fun(nodemay2019,countmay2019) #0.49
wmay2020 <- w_fun(nodemay2020,countmay2020) #0.41
waug2019 <- w_fun(nodeaug2019,countaug2019) #0.53
waug2020 <- w_fun(nodeaug2020,countaug2020) #0.46
wmar2019 <- w_fun(nodemar2019,countmar2019) #0.50
wmar2020 <- w_fun(nodemar2020,countmar2020) #0.49
wmar2021 <- w_fun(nodemar2021,countmar2021) #0.44
```



